Sea-ice and macrozooplankton distribution as determinants of top predator community structure in Antarctic winter

### 2024-06-06 analysis/paper/paper.qmd
Figure 3

make_fig_top6map(read_obj("topsix_clim_class", rast = TRUE))

@@

>>>>

make_fig_top6map(read_obj("topsix_clim_class", type = "rast"))

@@

```{r}
#| label: fig-seaice
#| fig-cap: "Distribution of sea ice coverage among sites, by predator cluster: (A) open water, (B) marginal ice, (C) pack ice. Dashed red line: median ice coverage."
#| out-width: 169mm
#| out-height: 121mm

make_fig_seaiceclust(read_obj("stations_clust"))
```
